Article Title

### 2019-10-04 Paper.tex
Added quality evaluation
New Datasets from Gramene
Fix some restructuring artefacts
Add a Gold Standard for barley and GOMAP dataset for Cotton
Add another quality evaluation metric: TC_AUCPCR
Restructure quantity table and add some real gene counts

\caption{\label{tab:cleanup-table}Number of removed annotations during cleanup.}
\centering
\begin{tabular}{llrr}
\toprule
Genome & Dataset & Obsolete Annotations & Duplicates\\
\midrule
\rowcolor{gray!6}  \textit{Glycine max} & GOMAP & 203 & 0\\
\cmidrule{1-4}
\textit{Hordeum vulgarum} & GOMAP & 101 & 0\\
\cmidrule{1-4}
\rowcolor{gray!6}  \textit{Medicago truncatula} A17 & GOMAP & 0 & 0\\
\cmidrule{1-4}
\textit{Medicago truncatula} R108 & GOMAP & 0 & 0\\
\cmidrule{1-4}
\rowcolor{gray!6}   & GOMAP & 111 & 2\\

\multirow{-2}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & GoldStandard & 38 & 556\\
\cmidrule{1-4}
\rowcolor{gray!6}  \textit{Phaseolus vulgaris} & GOMAP & 0 & 0\\
\cmidrule{1-4}
\textit{Triticum aestivum} & GOMAP & 285 & 0\\
\cmidrule{1-4}
\rowcolor{gray!6}  \textit{Vigna unguiculata} & GOMAP & 0 & 0\\
\cmidrule{1-4}
\textit{Zea mays} B73.v4 & GOMAP & 752 & 83\\
\cmidrule{1-4}
\rowcolor{gray!6}  \textit{Zea mays} Mo17 & GOMAP & 726 & 77\\
\cmidrule{1-4}
\textit{Zea mays} PH207 & GOMAP & 798 & 76\\
\cmidrule{1-4}
\rowcolor{gray!6}  \textit{Zea mays} W22 & GOMAP & 754 & 82\\
\cmidrule{1-4}
\textit{Arachis hypogaea} & GOMAP & 0 & 0\\
\cmidrule{1-4}
\rowcolor{gray!6}   & GOMAP & 1107 & 70\\

@@

\multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 54 & 0\\
\cmidrule{1-4}
\rowcolor{gray!6}   & Gramene61-IEA & 10 & 14\\

\multirow{-2}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-all & 48 & 9565\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:annotation-quantities}Quantitative metrics of the cleaned functional annotation sets. CC, BF, MP, and A refer to the aspects of the GO: Cellular Component, Biological Function, Molecular Process, and Any/All.}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}{lrlrrr>{\bfseries}r|rrr>{\bfseries}r|rrr>{\bfseries}r}
\toprule
\multicolumn{3}{c}{ } & \multicolumn{4}{c}{Annotations\textsuperscript{a}} & \multicolumn{4}{c}{Annotated Genes [\%]\textsuperscript{b}} & \multicolumn{4}{c}{Median Ann. per G.\textsuperscript{c}} \\
\cmidrule(l{3pt}r{3pt}){4-7} \cmidrule(l{3pt}r{3pt}){8-11} \cmidrule(l{3pt}r{3pt}){12-15}
Genome & Genes & Dataset & CC & BF & MP & A & CC & BF & MP & A & CC & BF & MP & A\\
\midrule
\rowcolor{gray!6}  \textit{Arachis hypogaea} &  & GOMAP & 153433 & 132944 & 493799 & 780176 & 57667 & 56855 & 67123 & 67124 & 2 & 2 & 6 & 10\\

\textit{Glycine max} &  & GOMAP & 129215 & 113827 & 417555 & 660597 & 46020 & 47034 & 52871 & 52872 & 2 & 2 & 6 & 11\\

\rowcolor{gray!6}  \textit{Hordeum vulgarum} &  & GOMAP & 88130 & 80282 & 272823 & 441235 & 35237 & 36470 & 39733 & 39734 & 2 & 2 & 5 & 10\\

\textit{Medicago truncatula} A17 &  & GOMAP & 107362 & 99719 & 364065 & 571146 & 42325 & 43736 & 50443 & 50444 & 2 & 2 & 6 & 10\\

\rowcolor{gray!6}  \textit{Medicago truncatula} R108 &  & GOMAP & 112343 & 108031 & 382322 & 602696 & 40332 & 50220 & 55706 & 55706 & 1 & 2 & 5 & 9\\

 &  & GOMAP & 72780 & 64685 & 248700 & 386165 & 28619 & 29853 & 35824 & 35825 & 2 & 2 & 6 & 9\\

\rowcolor{gray!6}   &  & GoldStandard & 7730 & 11060 & 19378 & 38176 & 5725 & 7383 & 9031 & 11387 & 1 & 1 & 1 & 3\\

 &  & Gramene61-IEA & 14633 & 32787 & 39105 & 86529 & 10771 & 15537 & 16705 & 21446 & 1 & 1 & 1 & 3\\

\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} &  & Gramene61-all & 20622 & 40674 & 54402 & 115710 & 13272 & 16962 & 18513 & 22272 & 1 & 1 & 2 & 4\\

\textit{Phaseolus vulgaris} &  & GOMAP & 72005 & 64583 & 229630 & 366218 & 25934 & 25539 & 27432 & 27433 & 2 & 2 & 6 & 11\\

\rowcolor{gray!6}  \textit{Triticum aestivum} &  & GOMAP & 267741 & 218623 & 785960 & 1272324 & 95604 & 98187 & 107890 & 107891 & 2 & 2 & 6 & 10\\

\textit{Vigna unguiculata} &  & GOMAP & 75867 & 68313 & 243278 & 387458 & 27173 & 27124 & 29772 & 29773 & 2 & 2 & 6 & 11\\

\rowcolor{gray!6}   &  & GOMAP & 135211 & 87420 & 291251 & 513882 & 34866 & 38073 & 39468 & 39469 & 3 & 2 & 6 & 11\\

 &  & GoldStandard & 1565 & 65 & 299 & 1929 & 1548 & 60 & 151 & 1634 & 1 & 0 & 0 & 1\\

\rowcolor{gray!6}   &  & Gramene49 & 20072 & 31056 & 30089 & 81217 & 11834 & 17991 & 15800 & 21926 & 1 & 1 & 1 & 3\\

\multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} &  & Phytozome & 4787 & 19044 & 13100 & 36931 & 4524 & 13728 & 11365 & 16132 & 0 & 1 & 1 & 2\\

\rowcolor{gray!6}  \textit{Zea mays} B73.v4 &  & GOMAP & 88827 & 82251 & 278719 & 449797 & 36717 & 37337 & 39323 & 39324 & 2 & 2 & 6 & 10\\

\textit{Zea mays} Mo17 &  & GOMAP & 87567 & 79214 & 277787 & 444568 & 33618 & 35105 & 38619 & 38620 & 2 & 2 & 6 & 10\\

\rowcolor{gray!6}  \textit{Zea mays} PH207 &  & GOMAP & 90617 & 85500 & 288677 & 464794 & 35170 & 36762 & 40556 & 40557 & 2 & 2 & 6 & 10\\

\textit{Zea mays} W22 & \multirow{-20}{*}{\raggedleft\arraybackslash 100} & GOMAP & 95390 & 85039 & 289780 & 470209 & 36987 & 37685 & 40689 & 40690 & 2 & 2 & 6 & 10\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[a] How many annotations in the CC, BF, and MP aspect does this dataset contain? A = How many in total? $\textrm{A} = \textrm{CC} + \textrm{BF} + \textrm{MP}$
\item[b] How many genes in the genome have at least one GO term from the CC, BF, MP aspect annotated to them? A = How many at least one from any aspect? ($\textrm{A} = \textrm{CC} \cup \textrm{BF} \cup \textrm{MP}$)
\item[c] Take a typical gene that is present in the annotation set. How many annotations does it have in each aspect? A = How many in total? Ask your favorite statistician why $\textrm{A} \neq \textrm{CC} + \textrm{BF} +\textrm{MP}$
\end{tablenotes}
\end{threeparttable}}
\end{table}

@@

\caption{\label{tab:quality-table}Quality evaluation of the used GO annotation sets.}
\centering
\begin{tabular}{llr}
\toprule
Genome & Dataset & SimGIC2 score\\
\midrule
\rowcolor{gray!6}   & GOMAP & 0.241470\\

 & GoldStandard & 0.999971\\

\rowcolor{gray!6}   & Gramene61-IEA & 0.324831\\

\multirow{-4}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-all & 0.732289\\
\cmidrule{1-3}
\rowcolor{gray!6}   & GOMAP & 0.072971\\

 & GoldStandard & 0.998562\\

\rowcolor{gray!6}   & Gramene49 & 0.126450\\

\multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 0.032693\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:cleanup-table}Number of removed annotations during cleanup.}
\centering
\begin{tabular}{llrr}
\toprule
Genome & Dataset & Obsolete Annotations & Duplicates\\
\midrule
\rowcolor{gray!6}  \textit{Brachypodium distachyon} & GOMAP & 696 & 43\\
\cmidrule{1-4}
\textit{Gossypium raimondii} & GOMAP & 184 & 0\\
\cmidrule{1-4}
\rowcolor{gray!6}  \textit{Hordeum vulgarum} & GoldStandard & 0 & 4\\
\cmidrule{1-4}
\textit{Medicago truncatula} A17 & GOMAP & 0 & 0\\
\cmidrule{1-4}
\rowcolor{gray!6}  \textit{Medicago truncatula} R108 & GOMAP & 0 & 0\\
\cmidrule{1-4}
 & GOMAP & 111 & 2\\

\rowcolor{gray!6}   & GoldStandard & 38 & 556\\

\multirow{-3}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-IEA & 10 & 14\\
\cmidrule{1-4}
\rowcolor{gray!6}  \textit{Phaseolus vulgaris} & GOMAP & 0 & 0\\
\cmidrule{1-4}
\textit{Sorghum bicolor} & GOMAP & 690 & 59\\
\cmidrule{1-4}
\rowcolor{gray!6}   & GOMAP & 285 & 0\\

 & GoldStandard & 0 & 10\\

\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & Gramene61-IEA & 47 & 48\\
\cmidrule{1-4}
\textit{Vigna unguiculata} & GOMAP & 0 & 0\\
\cmidrule{1-4}
\rowcolor{gray!6}   & GOMAP & 1107 & 70\\

@@

\multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 54 & 0\\
\cmidrule{1-4}
\rowcolor{gray!6}   & GOMAP & 752 & 83\\

 & GoldStandard & 55 & 174\\

\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & Gramene61-IEA & 99 & 157\\
\cmidrule{1-4}
\textit{Zea mays} Mo17 & GOMAP & 726 & 77\\
\cmidrule{1-4}
\rowcolor{gray!6}  \textit{Zea mays} PH207 & GOMAP & 798 & 76\\
\cmidrule{1-4}
\textit{Zea mays} W22 & GOMAP & 754 & 82\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:annotation-quantities}Quantitative metrics of the cleaned functional annotation sets. CC, BF, MP, and A refer to the aspects of the GO: Cellular Component, Biological Function, Molecular Process, and Any/All.}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}{lrlrrr>{\bfseries}r|rrr>{\bfseries}r|rrr>{\bfseries}r}
\toprule
\multicolumn{3}{c}{ } & \multicolumn{4}{c}{Genes Annotated[\%]\textsuperscript{a}} & \multicolumn{4}{c}{Annotations\textsuperscript{b}} & \multicolumn{4}{c}{Median Ann. per G.\textsuperscript{c}} \\
\cmidrule(l{3pt}r{3pt}){4-7} \cmidrule(l{3pt}r{3pt}){8-11} \cmidrule(l{3pt}r{3pt}){12-15}
Genome & Genes & Dataset & CC & BF & MP & A & CC & BF & MP & A & CC & BF & MP & A\\
\midrule
\rowcolor{gray!6}  \textit{Arachis hypogaea} & 67,124 & GOMAP & 85.91 & 84.70 & 100.00 & 100.00 & 153,433 & 132,944 & 493,799 & 780,176 & 2 & 2 & 6 & 10\\
\cmidrule{1-15}
\textit{Brachypodium distachyon} & 100 & GOMAP & 27,923.00 & 29,292.00 & 34,309.00 & 34,310.00 & 75,877 & 69,709 & 255,807 & 401,393 & 2 & 2 & 6 & 10\\
\cmidrule{1-15}
\rowcolor{gray!6}  \textit{Glycine max} & 52,872 & GOMAP & 87.04 & 88.96 & 100.00 & 100.00 & 129,215 & 113,827 & 417,555 & 660,597 & 2 & 2 & 6 & 11\\
\cmidrule{1-15}
\textit{Gossypium raimondii} & 100 & GOMAP & 34,908.00 & 34,651.00 & 37,504.00 & 37,505.00 & 96,793 & 85,511 & 307,921 & 490,225 & 2 & 2 & 6 & 11\\
\cmidrule{1-15}
\rowcolor{gray!6}   &  & GOMAP & 88.68 & 91.79 & 100.00 & 100.00 & 88,130 & 80,282 & 272,823 & 441,235 & 2 & 2 & 5 & 10\\

\multirow{-2}{*}{\raggedright\arraybackslash \textit{Hordeum vulgarum}} & \multirow{-2}{*}{\raggedleft\arraybackslash 39,734} & GoldStandard & 0.02 & 0.05 & 0.05 & 0.07 & 7 & 23 & 45 & 75 & 0 & 1 & 1 & 2\\
\cmidrule{1-15}
\rowcolor{gray!6}  \textit{Medicago truncatula} A17 & 50,444 & GOMAP & 83.90 & 86.70 & 100.00 & 100.00 & 107,362 & 99,719 & 364,065 & 571,146 & 2 & 2 & 6 & 10\\
\cmidrule{1-15}
\textit{Medicago truncatula} R108 & 55,706 & GOMAP & 72.40 & 90.15 & 100.00 & 100.00 & 112,343 & 108,031 & 382,322 & 602,696 & 1 & 2 & 5 & 9\\
\cmidrule{1-15}
\rowcolor{gray!6}   &  & GOMAP & 79.89 & 83.33 & 100.00 & 100.00 & 72,780 & 64,685 & 248,700 & 386,165 & 2 & 2 & 6 & 9\\

 &  & GoldStandard & 15.98 & 20.61 & 25.21 & 31.79 & 7,730 & 11,060 & 19,378 & 38,176 & 1 & 1 & 1 & 3\\

\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & \multirow{-3}{*}{\raggedleft\arraybackslash 35,825} & Gramene61-IEA & 30.07 & 43.37 & 46.63 & 59.86 & 14,633 & 32,787 & 39,105 & 86,529 & 1 & 1 & 1 & 3\\
\cmidrule{1-15}
\textit{Phaseolus vulgaris} & 27,433 & GOMAP & 94.54 & 93.10 & 100.00 & 100.00 & 72,005 & 64,583 & 229,630 & 366,218 & 2 & 2 & 6 & 11\\
\cmidrule{1-15}
\rowcolor{gray!6}  \textit{Sorghum bicolor} & 100 & GOMAP & 28,154.00 & 29,353.00 & 34,128.00 & 34,129.00 & 76,689 & 70,190 & 259,413 & 406,292 & 2 & 2 & 6 & 10\\
\cmidrule{1-15}
 &  & GOMAP & 88.61 & 91.01 & 100.00 & 100.00 & 267,741 & 218,623 & 785,960 & 1,272,324 & 2 & 2 & 6 & 10\\

\rowcolor{gray!6}   &  & GoldStandard & 0.89 & 0.57 & 1.54 & 1.73 & 1,590 & 923 & 4,807 & 7,323 & 1 & 0 & 2 & 3\\

\multirow{-3}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & \multirow{-3}{*}{\raggedleft\arraybackslash 107,891} & Gramene61-IEA & 26.74 & 55.24 & 48.72 & 70.24 & 38,975 & 109,319 & 109,518 & 257,832 & 0 & 1 & 1 & 2\\
\cmidrule{1-15}
\rowcolor{gray!6}  \textit{Vigna unguiculata} & 29,773 & GOMAP & 91.27 & 91.10 & 100.00 & 100.00 & 75,867 & 68,313 & 243,278 & 387,458 & 2 & 2 & 6 & 11\\
\cmidrule{1-15}
 &  & GOMAP & 34,866.00 & 38,073.00 & 39,468.00 & 39,469.00 & 135,211 & 87,420 & 291,251 & 513,882 & 3 & 2 & 6 & 11\\

\rowcolor{gray!6}   &  & GoldStandard & 1,548.00 & 60.00 & 151.00 & 1,634.00 & 1,565 & 65 & 299 & 1,929 & 1 & 0 & 0 & 1\\

 &  & Gramene49 & 11,834.00 & 17,991.00 & 15,800.00 & 21,926.00 & 20,072 & 31,056 & 30,089 & 81,217 & 1 & 1 & 1 & 3\\

\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} &  & Phytozome & 4,524.00 & 13,728.00 & 11,365.00 & 16,132.00 & 4,787 & 19,044 & 13,100 & 36,931 & 0 & 1 & 1 & 2\\

 &  & GOMAP & 36,717.00 & 37,337.00 & 39,323.00 & 39,324.00 & 88,827 & 82,251 & 278,719 & 449,797 & 2 & 2 & 6 & 10\\

\rowcolor{gray!6}   &  & GoldStandard & 8,349.00 & 10,067.00 & 12,120.00 & 14,971.00 & 11,510 & 15,019 & 25,737 & 52,428 & 1 & 1 & 1 & 3\\

\multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} &  & Gramene61-IEA & 14,774.00 & 22,064.00 & 23,965.00 & 29,152.00 & 20,265 & 47,657 & 58,110 & 126,525 & 1 & 1 & 2 & 3\\

\rowcolor{gray!6}  \textit{Zea mays} Mo17 &  & GOMAP & 33,618.00 & 35,105.00 & 38,619.00 & 38,620.00 & 87,567 & 79,214 & 277,787 & 444,568 & 2 & 2 & 6 & 10\\

\textit{Zea mays} PH207 &  & GOMAP & 35,170.00 & 36,762.00 & 40,556.00 & 40,557.00 & 90,617 & 85,500 & 288,677 & 464,794 & 2 & 2 & 6 & 10\\

\rowcolor{gray!6}  \textit{Zea mays} W22 & \multirow{-10}{*}{\raggedleft\arraybackslash 100} & GOMAP & 36,987.00 & 37,685.00 & 40,689.00 & 40,690.00 & 95,390 & 85,039 & 289,780 & 470,209 & 2 & 2 & 6 & 10\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[a] How many genes in the genome have at least one GO term from the CC, BF, MP aspect annotated to them? A = How many at least one from any aspect? ($\textrm{A} = \textrm{CC} \cup \textrm{BF} \cup \textrm{MP}$)
\item[b] How many annotations in the CC, BF, and MP aspect does this dataset contain? A = How many in total? $\textrm{A} = \textrm{CC} + \textrm{BF} + \textrm{MP}$
\item[c] Take a typical gene that is present in the annotation set. How many annotations does it have in each aspect? A = How many in total? Ask your favorite statistician why $\textrm{A} \neq \textrm{CC} + \textrm{BF} +\textrm{MP}$
\end{tablenotes}
\end{threeparttable}}
\end{table}

@@

\caption{\label{tab:quality-table}Quality evaluation of the used GO annotation sets.}
\centering
\begin{tabular}{llrr}
\toprule
Genome & Dataset & SimGIC2 score & TC AUCPCR score\\
\midrule
\rowcolor{gray!6}  \textit{Hordeum vulgarum} & GOMAP & 0.158996 & 0.000477\\
\cmidrule{1-4}
 & GOMAP & 0.253680 & 0.204084\\

\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-IEA & 0.330437 & 0.193740\\
\cmidrule{1-4}
 & GOMAP & 0.218996 & 0.010039\\

\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & Gramene61-IEA & 0.175564 & 0.005397\\
\cmidrule{1-4}
 & GOMAP & 0.052182 & 0.012709\\

\rowcolor{gray!6}   & Gramene49 & 0.091475 & 0.019127\\

\multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 0.028721 & 0.004498\\
\cmidrule{1-4}
\rowcolor{gray!6}   & GOMAP & 0.257543 & 0.196845\\

\multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & Gramene61-IEA & 0.328777 & 0.188584\\
\bottomrule
\end{tabular}
\end{table}

### 2019-10-04 text/03-results.Rmd
Restructure quantity table and add some real gene counts

```{r annotation-quantities}
dt2 <- read.csv("../analyses/quantity/results/quantity_table.csv", header=T, stringsAsFactors=F)
# Format the genome names according to conventions
dt2$genome = format_genome(dt2$genome)
# Drop the absolute 'genes annotated' counts, we only want the percentual ones
dt2 <- dt2[, !names(dt2) %in% c("genes_annotated_c", "genes_annotated_f", "genes_annotated_p", "genes_annotated_a")]
headers_above = c(a = 3, b = 4, c = 4, d =4)
names(headers_above) <- c(" ", 
  paste0("Annotations", footnote_marker_alphabet(1, double_escape=T)),
  paste0("Annotated Genes [\\\\%]", footnote_marker_alphabet(2, double_escape=T)), 
  paste0("Median Ann. per G.", footnote_marker_alphabet(3, double_escape=T)))
kable(dt2, booktabs=T, escape=F, caption = "Quantitative metrics of the cleaned functional annotation sets. CC, BF, MP, and A refer to the aspects of the GO: Cellular Component, Biological Function, Molecular Process, and Any/All.", col.names=c("Genome", "Genes", "Dataset", "CC", "BF", "MP", "A","CC", "BF", "MP", "A","CC", "BF", "MP", "A")) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  add_header_above(headers_above, escape=F)%>%
  column_spec(c(15), bold = T) %>%
  column_spec(c(7,11), bold=T, border_right = T) %>%
  collapse_rows(columns = 1:2, latex_hline="major") %>%
  footnote(alphabet=c(
    "How many annotations in the CC, BF, and MP aspect does this dataset contain? A = How many in total? $\\\\textrm{A} = \\\\textrm{CC} + \\\\textrm{BF} + \\\\textrm{MP}$",
    "How many genes in the genome have at least one GO term from the CC, BF, MP aspect annotated to them? A = How many at least one from any aspect? ($\\\\textrm{A} = \\\\textrm{CC} \\\\cup \\\\textrm{BF} \\\\cup \\\\textrm{MP}$)",
    "Take a typical gene that is present in the annotation set. How many annotations does it have in each aspect? A = How many in total? Ask your favorite statistician why $\\\\textrm{A} \\\\neq \\\\textrm{CC} + \\\\textrm{BF} +\\\\textrm{MP}$"
  ), threeparttable=T, escape=F)
```

>>>>

```{r annotation-quantities}
dt2 <- read.csv("../analyses/quantity/results/quantity_table.csv", header=T, stringsAsFactors=F)
# Format the genome names according to conventions
dt2$genome = format_genome(dt2$genome)
# Drop the absolute 'genes annotated' counts, we only want the percentual ones
dt2 <- dt2[, !names(dt2) %in% c("genes_annotated_c", "genes_annotated_f", "genes_annotated_p", "genes_annotated_a")]
headers_above = c(a = 3, b = 4, c = 4, d =4)
names(headers_above) <- c(" ", 
  paste0("Genes Annotated[\\\\%]", footnote_marker_alphabet(1, double_escape=T)), 
  paste0("Annotations", footnote_marker_alphabet(2, double_escape=T)),
  paste0("Median Ann. per G.", footnote_marker_alphabet(3, double_escape=T)))
kable(dt2, booktabs=T, digits=2, format.args=list(big.mark=","), escape=F, caption = "Quantitative metrics of the cleaned functional annotation sets. CC, BF, MP, and A refer to the aspects of the GO: Cellular Component, Biological Function, Molecular Process, and Any/All.", col.names=c("Genome", "Genes", "Dataset", "CC", "BF", "MP", "A","CC", "BF", "MP", "A","CC", "BF", "MP", "A")) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  add_header_above(headers_above, escape=F)%>%
  column_spec(c(15), bold = T) %>%
  column_spec(c(7,11), bold=T, border_right = T) %>%
  collapse_rows(columns = 1:2, latex_hline="major") %>%
  footnote(alphabet=c(
    "How many genes in the genome have at least one GO term from the CC, BF, MP aspect annotated to them? A = How many at least one from any aspect? ($\\\\textrm{A} = \\\\textrm{CC} \\\\cup \\\\textrm{BF} \\\\cup \\\\textrm{MP}$)",
    "How many annotations in the CC, BF, and MP aspect does this dataset contain? A = How many in total? $\\\\textrm{A} = \\\\textrm{CC} + \\\\textrm{BF} + \\\\textrm{MP}$",
    "Take a typical gene that is present in the annotation set. How many annotations does it have in each aspect? A = How many in total? Ask your favorite statistician why $\\\\textrm{A} \\\\neq \\\\textrm{CC} + \\\\textrm{BF} +\\\\textrm{MP}$"
  ), threeparttable=T, escape=F)
```
